\mythesistitleNOTSYNPOSIS

### 2012-01-04 src/020chap2.tex
Reordered chrono.
Added amsthm and changed theorem environs to comply.
Added atbeginend commands to space theorem environs.
Added a few \def strings.

Added placeholders for a couple of definitions.

Started editing. Intro. Added a couple of definitions.

Minor edits to comply with amsthm

Spacing hacks mostly.

Trivial.

\chapter{Consecutive-ones Property - a Survey of Important Results}
\label{ch:copsurvey}
\tnote{[i] TBD: have a few lines about organization of chapter\ \ \ \
  \ [ii] Survey chapter: is the full fledged expansion of the survey in
  introduction with details, observations, theorems etc.}

\section*{-- REAL CONTENT --}

>>>>

\chapter{\CoP\,-- A Survey of Important Results}
\label{ch:copsurvey}

This chapter surveys several results that are significant to this
thesis or to \COP in general. These predominantly pertain to
characterizations of \COP, algorithmic tests to check for \COP (COT),
optimization problems on binary matrices that do not have \COP and
some applications of \COP.

\tnote[important]{ADD: have a few lines about organization of chapter}

\tnote{DEFINE COP SOMEWHERE}

\section{\COP in Graph Theory}

\COP is closely connected to several types of graphs by way of
describing certain combinatorial graph properties. There are also
certain graphs, like convex bipartite graphs, that are defined solely
by some of its associated matrix having \COP.  In this section we will
see the relevance of \cop to graphs.  To see this we introduce certain
binary matrices that are used to define graphs in different
ways. While adjacency matrix is perhaps the most commonly used such
matrix, Definition~\ref{def:graphmatrices} defines this and a few
more.

\begin{definition}{\emph{Matrices that define
      graphs.\cite[Def.~2.4]{d08phd}}} %
  \label{def:graphmatrices} %
  Let $G$ and $H$ be defined as follows. $G = (V,E_G)$ is a graph with
  vertex set $V = \{v_i \mid i \in [n]\}$ and edge set $E_G \subseteq
  \{(v_i,v_j) \mid i, j \in [n]\}$ such that $|E_G| = m$. $H = (A, B,
  E_H)$ is a bipartite graph with partitions $A = \{a_i \mid i \in
  [n_a]\}$ and $B = \{b_i \mid i \in [n_b]\}$.
  \begin{enumerate}[{\ref{def:graphmatrices}}--i.]
  \item \emph{Adjacency matrix} of $G$ is the symmetric $n \times n$
    binary matrix $M$ with $m_{i,j} = \un$ \iff $(v_i,v_j) \in E_G$
    for all $i,j \in [n]$.
  \item \emph{Augmented adjacency matrix} of $G$ is obtained from its
    adjacency matrix by setting all main diagonal elements to \un, \ie
    $m_{i,i} = \un$ for all $i \in [n]$.
  \item \emph{Maximal clique matrix} or \emph{vertex-clique incidence
      matrix} of $G$ is the $n \times k$ binary matrix $M$ with
    $m_{i,j} = \un$ \iff $v_i \in C_j$ for all $i \in [n], j \in [k]$
    where $\{C_j \mid j \in [k]\}$ is the set of maximal cliques of
    $G$.
  \item \emph{Half adjacency matrix} of $H$ is the $n_a \times n_b$
    binary matrix $M$ with $m_{i,j} = \un$ \iff $(a_i, b_j) \in E_H$
  \end{enumerate}
\end{definition}

Now we will see in Definition~\ref{def:graphwithcop} certain graph
classes that is related to \COP or \CROP.\\

%\hrule
\begin{definition}{\emph{Graphs that relate to
      COP.\cite[Def.~2.5]{d08phd}}} %
   \label{def:graphwithcop} %
   Let $G$ be a graph and $H$ be a bipartite graph.

   \begin{enumerate}[\ref{def:graphwithcop}--i.]
   \item $G$ is \emph{convex-round} if its adjacency matrix has the
     \CROP.
   \item $G$ is \emph{concave-round} if its augmented adjacency matrix
     has \CROP. \tnote{cite BHY00} \tnote[minor]{add CROP to glossary}
   \item $G$ is an \emph{interval graph} if its vertices can be mapped
     to intervals on the real line \stt two vertices are adjacent \iff
     their corresponding intervals overlap \tnote{cite Ben59, Haj57}.
     $G$ is an interval graph \iff its maximal clique matrix has COP
     due to the result by \cite{gh64} which states that the maximal
     cliques of interval graph $G$ can be linearly ordered \stt for
     all $v \in V(G)$, cliques containing $v$ are consecutive in the
     ordering.
   \item $G$ is a \emph{unit interval graph} if it is an interval
     graph \stt all intervals have the same length.
   \item $G$ is a \emph{proper interval graph} if it is an interval
     graph \stt no interval properly contains another.
   \item $G$ is a \emph{circular-arc graph} if its vertices can be
     mapped to a set of arcs on a circle \stt two vertices are
     adjacent \iff their corresponding arcs overlap.
   \item $H$ is \emph{convex bipartite} if its half adjacency matrix
     has \COP on either rows or columns.
   \item $H$ is \emph{biconvex bipartite} or \emph{doubly
       convex}\cite{yc95} if its half adjacency matrix has \COP on
     both rows and columns.
   \item $H$ is \emph{circular convex} if its half adjacency matrix
     has \CROP.
   \end{enumerate}
\end{definition}
%\hrule
